\newcommand{\conclusionstitle}{Conclusions and outlook}
\chapter*{\conclusionstitle}
\addcontentsline{toc}{chapter}{\conclusionstitle}
\markboth{\uppercase{\conclusionstitle}}{\uppercase{\conclusionstitle}}

The Standard Model (SM) of particle physics successfully describes the
phenomenology at the Large Hadron Collider which can be observed by
general purpose detectors, the Compact Muon Solenoid (CMS) and
the Toroidal LHC ApparatuS (ATLAS).

While the discovery of the Higgs Boson in 2012 completed the particle content of the theory,
several of its predictions remain untested to high accuracy.
Accordingly, the physics programme of both general purpose detectors
started to focus increasingly on high precision measurements.
In this context, non-abelian electroweak couplings are prime candidates,
because of their role in preserving the unitarity for certain classes of processes involving the Higgs boson,
and because of the large number of Beyond Standard Model scenarios that predict their enhancement.

The non-abelian triple and quartic gauge couplings are involved in several processes
that can be observed at a particle collider,
including the simultaneous production of three vector bosons.
The search for triboson production is experimentally very challenging
because of the small production cross section predicted by the SM,
which results in a low event yield.

I designed the global strategy of this analysis, which is a search for
the simultaneous production of three electroweak bosons,
either two \PZ bosons and a photon or one \PZ boson, one \PW boson and a photon,
in three orthogonal channels with four, three and two charged leptons respectively.
This study is conducted using data collected at a centre-of-mass energy of 13\TeV
by the CMS detector in the 2016--2018 period (\Run2),
corresponding to an integrated luminosity of $137.6 \fbinv$.

The focus of my work during the PhD is on the four lepton channel,
which targets both the inclusive production of four charged isolated leptons and a photon
and the triboson production of two Z bosons, which decay leptonically, and a photon.
The cross sections of the inclusive production
of four leptons, either electrons or muons, and a photon,
is measured in the phase space of interest
$\sigma(\Pp\Pp \to 4\Pl\PGg) = 13.5{}^{+5.4}_{-4.7}\usep\text{fb}$.
%% This is $\mu \times \sigma_{\rm sample}^{\PZ\PZ\PGg}$, see Section~\ref{sec:likelihood_scans_inclusive}.
The observed (expected) significance of this process over the background-only hypothesis
is assessed to be $6.1\usep\sigma$ ($5.5\usep\sigma$).

Evidence was found for the production of two \PZ bosons and a photon
in the fiducial region where the SM contribution from final-state radiation photons is suppressed.
Its cross section, extracted with a maximum likelihood fit, is
$\sigma(\Pp\Pp \to \PZ\PZ\PGg \to 4\Pl\PGg) = 4.9{}^{+2.7}_{-2.1}\usep\text{fb}$.
The observed (expected) significance of the $\PZ\PZ\PGg$ production over the hypothesis of only background
is $3.0\usep\sigma$ ($3.5\usep\sigma$).

Preliminary results in the three lepton channel for the production of
three leptons, one neutrino and a photon
in proton-proton collisions are also presented.
The expected significance of the signal hypothesis is above 3 standard deviations.

The status of the two lepton channel is not yet at a point where results can be derived with reasonable confidence,
but preparatory work was done by a bachelor student which I helped supervise,
and will be followed up in the near future.

All the results in this analysis suffer from the low cross section of the processes involved, and would benefit greatly
from the inclusion of the data from the currently ongoing \Run3, which started in 2022,
and even more from the data that will be collected with the upcoming High Luminosity phase of LHC.

My personal contribution covers almost every aspect of the analysis,
starting from the design of the division into three channels.
I studied the simulation of the signal samples for the semileptonic channel,
including their validation, and followed their production.

After implementing the most recent calibrations of the data and simulation,
I studied several identification criteria for photons and their performance.
I also devised the data-driven estimation strategy for the background
from \nonprompt photons and jets misidentified as photons.
The separation of the triboson component and FSR component,
both in the signal and in the main background,
was also carefully investigated, with special care for the four lepton channel.

I examined all of the sources of systematic uncertainty in the analysis,
assessing their effect on the shape and yield of the signal and main backgrounds,
including their effect in the statistical model used to derive the results.
I established and tested various strategies for the statistical inference,
accounting for the systematic uncertainties, and compared their performance and stability.

The combination of all three channels for $\PZ\PZ\PGg$ and $\PW\PZ\PGg$, both semi- and fully-leptonic,
will allow us to increase the sensitivity, possibly up to the threshold for the observation
of these triboson production processes.
Unlike the four lepton channel, the others have a higher event yield and could benefit
from more effective techniques for background rejection,
such as machine learning methods, to boost the sensitivity to the signal.

An interpretation of this analysis in the context of the Standard Model Effective Field Theory %~\todo{citation}
would provide insight and possibly help constraining several bosonic operators,
in connection with the ongoing effort within the CMS Collaboration to perform a global fit. %~\todo{cite CMS SMEFT combination, if any (?)}.
As part of this endeavour, I contributed to a parton-level study~\cite{Bellan_2023}
on the effect of a set of bosonic dimension-6 operators on triboson production in several channels.
This study, which explored the correlations between the different operators and the complementarity
of the various channels, as well as the most sensitive observables, provides
a benchmark for the design and coordination of present and future analysis efforts.

Within the CMS collaboration, I also took part to several experimental activities.
I participated in data-taking during 2022 as a shifter for the Data Acquisition system,
and also as a ``detector on call'', that is the point of contact between the experts of
a subdetector and the central CMS shifters in charge of data taking.

I also participated to the tracker alignment activities,
including performing several alignment campaigns,
both for the derivation of the conditions at startup and after environmental changes
and to provide optimal calibrations for the reprocessing campaigns at the end of the year.
I also conducted the validation of many alignment candidates to assess their performance
and evaluate the impact of their application for online data taking.

I also worked on the muon reconstruction, implementing the possibility to redo
the pattern recognition in the muon chambers during the global reconstruction,
starting from seeds produced by the tracks from the inner tracker.
