\section{Event Selection}
\label{sec:event_selection}

\textbf{Z candidates} are defined as pairs of selected leptons (eletrons or muons) with same flavour and opposite sign (SFOS).
They must satisfy $60 < m_{\Pl\Pl} < 120 \GeVcc$, where the Z candidate mass includes any selected FSR photons associated to its leptons.

In the 4\Pl channel, \textbf{ZZ candidates} are built from pairs of Z candidates with no lepton in common.
The first Z candidate $\PZ_1$ is chosen as the one with the reconstructed mass $m_{\Pl\Pl}$ closest to the nominal Z mass.
The second candidate is called $\PZ_2$.
The ZZ candidates are required to satisfy the following:
\begin{itemize}
\item Ghost removal: each of the four leptons must have $\DR > 0.02$ with any of the others.
  This requirement excludes ``ghost tracks'' made with a fraction of the hits of another lepton that produce an additional spurious lepton candidate.
\item Lepton \pt: the most energetic lepton must have $\pt^1 > 20 \GeVc$ and the second most energetic $\pt^2 > 20 \GeVc$,
  in order to ensure a high and constant trigger efficiency for all the selected events.
\item Low mass resonance suppression: all four opposite sign pairs, regardless of flavour, that can be built must satisfy $m_{\Pl\Pl} > 12 \GeVcc$.
  This cut suppresses pairs of leptons from cascade decays, which may have different flavour and are found to broadly peak at very low invariant masses.
  In this case, selected FSR photons are not used in computing $m_{\Pl\Pl}$, since a QCD-induced low mass di-lepton (e.g. \JPsi) may have photons nearby (e.g. from a \Pgpz).
\item Wrong pairing suppression: in the 4\Pe and 4\PGm channels,
  defining $\PZ_a$ and $\PZ_b$ the mass-sorted alternative pairing of the four leptons ($\PZ_a$ is the closest to the nominal Z boson mass),
  the ZZ candidate is excluded if: $|m_{\PZ_a} - m_\PZ^{PDG}| < |m_{\PZ_1} - m_\PZ^{PDG}|$ AND $m_{\PZ_b} < 12 \GeVcc$.
  This cut suppresses contribution from events that are likely an on-shell Z and a low mass \Plp \Plm resonance,
  but would otherwise produce a valid $\PZ_1 \PZ_2$ combination with the alternative pairing.
\item Four-lepton invariant mass: $m_{4\Pl} > 100 \GeVcc$.
\end{itemize}
