\chapter{Results}
\label{sec:results}
\input{results/caption-commands.tex} % Template captions for results

In this chapter the results of
the measurement of the cross section of $\Pp\Pp \to 4\Pl \PGg$, as well as
the search for $\PZ\PZ\PGg$ triboson production are presented
in Sections~\ref{sec:results_4L_inclusive} and~\ref{sec:results_4L_FSRcut} respectively.
Preliminary results for the three lepton channel, focusing on the cross section of the $\Pp\Pp \to 3\Pl\PGnl\PGg$,
are also reported in Section~\ref{sec:results_3L}.
This analysis uses the data collected by the CMS experiment during the 2016--2018 period at a centre-of-mass energy of 13\TeV.
The analysis strategy is to search for excess events over the estimated background yield from known Standard Model processes.
Different identification strategies for the photon and several kinematic distributions are explored.

First the statistical tools used for the extraction of the parameters of interest and interpretation are described.
Then the expected result before unblinding is discussed, and the best strategy selected.
Finally, the observed results are shown.

\section{Yields and kinematic distributions}
\input{results/yields.tex}

\section{Statistical analysis}
\input{results/statistical.tex}

\section{Four lepton channel}
\label{sec:results_4L}
This section reports the results obtained for the four lepton channel, which is the focus of this thesis.

%% \subsection{Comparison of strategies}
\label{sec:strategy_description}
As mentioned in Sections \ref{sec:evt_photon_selection} and \ref{sec:FSR_cut},
different approaches are used to select the photon
and results are reported both with and without the cut suppressing the FSR contribution,
targeting the inclusive process and a photon and triboson production respectively.
Additionally, several event variables are tested for the final fit to the signal strength.

The first is the invariant mass of the $\PZ\PZ\PGg$ system.
It is expected to be higher for triboson events where the photon comes from
initial state radiation or a triple or quartic gauge coupling than for FSR.
Additionally, it is expected to be sensitive to Beyond Standard Model (BSM) contributions, especially in the high-energy tail.

The second variable is the transverse momentum of the photon.
As the $\PZ\PZ\PGg$ mass and the $\PW\PZ\PGg$ transverse mass,
it is presumed to be sensitive to BSM physics in the high-momentum tail.

The third option considered is the MVA-based ID working point passed by the photon.
In each event, the photon passing the highest MVA working point is selected.
Three bins are defined:
\begin{itemize}
\item \makebox[7em][l]{\bf wp80} The photon passes the \texttt{wp80} working point;
\item \makebox[7em][l]{\bf $\mathrm{wp90} \land \mathrm{!wp80}$} The photon passes \texttt{wp90}, but fails \texttt{wp80};
\item \makebox[7em][l]{\bf None} The photon fails \texttt{wp90};
\end{itemize}
The yield of the simulation in each bin is scaled according to the appropriate scale factors (see Section \ref{sec:photonID}).
This distribution is referred to as ``MVA shape''.

As discussed in Section~\ref{sec:samples_overlap},
only the events from the $\PQq\PAQq \to \PZ\PZ$ sample
that do not contain a prompt generated photon are used,
to avoid double counting with the signal sample $\PZ\PZ\PGg$.
Additionally, when the data-driven estimate of fake photons is employed,
events in $\PQq\PAQq \to \PZ\PZ$ and $\Pg\Pg \to \PZ\PZ$ that do not contain a prompt photon are excluded.

The data-driven estimate of the fake lepton background is employed in all strategies,
except when using the data-driven \nonprompt photons.
In that case, the fake leptons are included in the data-driven estimate of \nonprompt photons,
as discussed in Section~\ref{sec:backgrounds_in_SR},
and therefore the estimate from the leptonic control regions CR3P1F and CR2P2F is not added to the total background.

In particular, the following choices of the aforementioned analysis strategy were tested:
\begin{itemize}
\item Data-driven estimate of fake photons,
  using the Loose working point of the cut-based ID to select the signal photon,
  and performing the analysis on the invariant mass spectrum of the $\PZ\PZ\PGg$ system.
\item Fake photon prediction taken from simulation,
  using the Loose working point of the cut-based ID to select the signal photon,
  and performing the analysis on the invariant mass spectrum of the $\PZ\PZ\PGg$ system.
\item Fake photon prediction taken from simulation,
  using the Loose working point of the cut-based ID to select the signal photon,
  and performing the analysis on the transverse momentum distribution of the photon.
\item Fake photon prediction taken from simulation,
  using the \texttt{wp90} working point of the MVA-based ID to select the signal photon,
  and performing the analysis on the invariant mass spectrum of the $\PZ\PZ\PGg$ system.
\item Fake photon prediction taken from simulation,
  using the \texttt{wp90} working point of the MVA-based ID to select the signal photon,
  and performing the analysis on the transverse momentum distribution of the photon.
\item Fake photon prediction taken from simulation,
  using the \texttt{wp80} working point of the MVA-based ID to select the signal photon,
  and performing the analysis on the invariant mass spectrum of the $\PZ\PZ\PGg$ system.
\item Fake photon prediction taken from simulation,
  using the kinematic selection for the photons,
  and classifying events depending on which is the highest MVA working point passed by the photon.
\end{itemize}

For the strategies that do not use the data-driven estimate of \nonprompt photons,
additional uncertainties of $\approx 40\usep\%$ on the normalization
of the samples $\PQq\PAQq \to 4\Pl (\PGg_\text{NP})$ and $\Pg\Pg \to 4\Pl (\PGg_\text{NP})$ are added.
This uncertainty, which accounts for the mismodelling of this instrumental background in the simulation,
is implemented as a group of parameters scaling the normalization of the samples,
that are constrained by a log-normal probability density function with width parameter equal to 1.3.

First, expected results are derived for each strategy using an Asimov dataset~\cite{Cowan2011},
and the expected significances, signal strength modifiers and impacts of the systematic uncertainties are evaluated.
Then, the best performing strategy is selected and the results are derived using the actual data.

\subsection{Inclusive cross section}
\label{sec:results_4L_inclusive}
The first results pertain the measurement of the inclusive process $\Pp\Pp \to 4\Pl\PGg$ with $\Pl = \Pe,\,\PGm$.
All of the selections detailed in Section~\ref{sec:event_selection} for the four lepton channel are applied,
but the additional cut to suppress FSR is not.

\subsubsection{Significance}
\input{results/significance_table_inclusive.tex}
The expected significances of the various strategies for the identification of the photon and the estimation of the fake photon background
are illustrated in Table~\ref{tab:summary_significances_inclusive}.
The best results are obtained using the MVA ID for the photon, in particular the ``MVA shape''.
The choice of the variable for the fit does not have a large effect.
The cut-based selection results in a significance around 5\usep$\sigma$,
except for the data-driven estimation of the \nonprompt photon background,
while the MVA based ID results in an increase of around 0.5.

The sensitivity is limited by the amount of data, as discussed in Section~\ref{sec:likelihood_scans_inclusive},
which is in agreement with the observation that the various strategies have expected significances approximately in the same range.
Indeed, as reported in Table~\ref{tab:Run2_SR4P_phoCR_lepCR}, the expected yield in the signal region, using the Loose cut-based ID,
is $21.1 \pm 1.2$ events, of which $13.6 \pm 0.2$ from the signal sample.

\subsubsection{Cross section measurement}
\input{results/unblinded_4L_inclusive.tex}

\subsection{Triboson fiducial region}
\label{sec:results_4L_FSRcut}
The following results are derived after the application of the cut
designed to suppress FSR and enhance the fraction of events from triboson production diagrams,
described in Section~\ref{sec:FSR_cut}.
The target is the process $\Pp\Pp \to \PZ\PZ\PGg \to 4\Pl\PGg$.

\subsubsection{Significance}
The significances obtained with the various strategies for the identification of the photon
and the estimation of the fake photon background are illustrated in
Table~\ref{tab:summary_significances_FSRcut}.
\input{results/significance_table_FSRcut.tex}

The highest sensitivity is expected with
the data-driven estimation of the fake photon background.
The second best results are expected with the fit to the invariant mass of the $\PZ\PZ\PGg$ system,
selecting the photon with the \texttt{wp80} of the MVA ID,
and the binned MVA shape and the \texttt{wp90} (either $m_{\PZ\PZ\PGg}$ or $\pt^\PGg$)
have a similar expected performance.

The expected significance is below $3\usep\sigma$ for the cut-based selection,
except when using the data-driven estimate for \nonprompt photons,
while the MVA based selection results in 3.3--3.5\usep$\sigma$.
This region is heavily affected by the low event yield,
with only $6.8 \pm 0.2$ events expected with the cut-based photon ID,
of which $5.6 \pm 0.1$ from the signal sample,
as shown in Table~\ref{tab:yield_SR4P_1P_FSRcut_Loose}.

\subsubsection[Search for triboson ZZgamma production]{Search for triboson $\PZ\PZ\PGg$ production}
\input{results/unblinded_4L_FSRcut.tex}

\section{Three lepton channel}
\label{sec:results_3L}
The results reported in this section are the preliminary findings
of the work dedicated to this channel.
The variable chosen for the template fit is the transverse mass of the $\PW\PZ\PGg$ system,
which is defined as:
\begin{equation}
  \label{eq:transverse_mass}
  \mT^2 \mathdefined E^2 - p_z^2 = m^2 + \ptvec^{\:2}
\end{equation}
This quantity is used instead of the invariant mass because only the transverse component of the neutrino momentum is measured,
albeit indirectly through the missing energy.
While it is possible to calculate the z-component of the neutrino momentum assuming that the \PW mass is exactly on the peak,
this would introduce an additional bias with no benefit on the sensitivity.

As discussed in Section~\ref{sec:samples_overlap},
the events that contain a prompt generated photon from the
$\PQq\PAQq\to\PZ\PZ$, $\PW\PZ\to3\Pl\PGn$ and Drell-Yan samples are discarded,
to avoid double counting with the signal samples $\PZ\PZ\PGg$, $\PW\PZ\PGg$ and with $\PZ\PGg$.
When the data-driven estimation of fake photon is employed,
events from the samples $\PQq\PAQq\to\PZ\PZ$, $\Pg\Pg\to\PZ\PZ$, $\PW\PZ\to3\Pl\PGn$ and Drell-Yan
without a prompt generated photon are excluded as well.

The photon is selected using the Loose working point of the cut-based ID.
Two strategies are compared:
\begin{itemize}
\item Data-driven estimate of fake photons,
  using the Loose working point of the cut-based ID to select the signal photon,
  and performing the analysis on the transverse mass spectrum of the $\PW\PZ\PGg$ system.
\item Fake photon and lepton predictions taken from simulation,
  using the Loose working point of the cut-based ID to select the signal photon,
  and performing the analysis on the transverse mass spectrum of the $\PW\PZ\PGg$ system.
\end{itemize}

\subsection{Inclusive cross section}
The following results target the inclusive production of
$\Pp\Pp \to 3\Pl\, \PGnl\, \PGg$, with $\Pl = \Pe, \PGm$.
Thus the cut designed to suppress the contributions from genuine photons from FSR is not applied.

\subsubsection{Significance}
The expected sensitivity for the \RunII{} period
using the data-driven estimate of \nonprompt and misidentified photons is
$3.67 \sigma$,
while the result expected using the prediction from the simulation is
$3.06 \sigma$.
This is consistent with the event yields in Tables~\ref{tab:Run2_SR3P_phoCR_lepCR} and~\ref{tab:Run2_SR3P_phoMC_lepCR},
which show different predictions for the background yields in the signal region.

\subsubsection{Likelihood scans}
\input{results/likelihood_scans_SR3P_inclusive.tex}

\subsubsection{Systematic impacts}
\input{results/impacts_SR3P_inclusive.tex}
