\chapter{Analysis Strategy}
\label{sec:strategy}
The analysis aims at observing triboson production of $\PZ\PZ\PGg$ and $\PW\PZ\PGg$, by combining three orthogonal channels.
The \textit{channels} are defined based on the number of leptons in the event.
The four charged lepton channel (4\Pl) targets the $\PZ\PZ\PGg$ production with fully leptonic decay of the two Z bosons.
The three charged lepton channel (3\Pl) is designed primarily for the $\PW\PZ\PGg$ production, in the fully leptonic decay channel of the \PW and \PZ bosons.
Finally, the two charged lepton channel (2\Pl) targets both the $\PZ\PZ\PGg$ and $\PW\PZ\PGg$ production, where one \PZ decays to leptons,
and the other massive boson decays to quarks, which hadronize to jets.

Each channel is studied using several \textit{regions},
based on the number of leptons that pass the tight selection %(Sections \ref{sec:ele_selection} and \ref{sec:muo_selection}),
and whether or not there is a photon that passes the tight selection. %(Section \ref{sec:photonID}).

The main results reported in this analysis are for the four lepton channel,
while only preliminary findings on the three lepton channel and preparatory studies for the two lepton channel are described.
My contribution to the analysis includes the architecture of the overall strategy in three orthogonal channels,
the \nonprompt photon background study, its estimation technique and its application to the three channels
and the full analysis of the $4\Pl+\PGg$ channel.

\section{Signal}
\input{strategy/signal}

\section{Background}
\input{strategy/backgrounds}

\section{Event selection}
\input{strategy/event_selection}

\section{Background estimation strategy}
I devised a set of background estimation strategies mainly for misidentified and \nonprompt particles that are common to the three channels.
The consequent division into Signal Regions (SR), Control/application Regions (CR) and measurement region is illustrated in Table~\ref{tab:region_definition}.
\input{strategy/region_table.tex}

\subsection{Fake leptons}
\input{strategy/fake_lepton_estimation}
\subsection{Fake photons}
\input{strategy/fake_photon_estimation}

\subsection{Application to the signal region}
\input{strategy/backgrounds_in_SR}

\input{strategy/datasets}

\input{strategy/systematics}

\begin{subappendices}
  \section{APV25 preamplifier saturation}
  \input{body/APV.tex}
\end{subappendices}
